\begin{abstract}
Detecting hallucinations in Large Language Model-generated text is crucial for
their safe deployment. Recent mechanistic approaches show promise by using
internal hidden states as uncertainty signals, but they face two important
limitations. Some methods probe only isolated layer--token positions, missing
uncertainty signals distributed across layers and generated tokens. Others
process richer activation tensors but are not equipped for long-form
generation -- pooling over the token axis collapses the signal as responses
grow longer -- or are too inefficient to run as tokens are produced. In this
paper, we introduce a temporal uncertainty localization framework that
detects hallucinations in real time by predicting which generated-token
regions carry the hidden-state activation patterns most indicative of
uncertainty. Because generated sequences range from a handful of tokens to
thousands, we treat the layer--token activation tensor as a \emph{video} over
the token axis rather than a single fixed-size image: each generated token is
a frame whose height is the layer axis and whose channels are the hidden
dimension, and a window aggregates the activations of consecutive tokens.
Since clean hallucination labels are typically available only at the
full-response level, we train our model using weak supervision: a frozen
ACT-ViT encoder
extracts uncertainty-aware features from local activation windows, and a
Mamba-based temporal head assigns uncertainty logits to each window. A
top-$k$ multiple-instance learning objective aggregates the most uncertain
windows into a sequence-level prediction, enabling localization without
window-level labels. Our approach decomposes training into three stages:
(i) we learn activation patterns predictive of uncertainty at the
sequence level, (ii) we freeze the encoder and train the temporal head to
localize suspicious windows on per-atom segments under sequence-level
supervision, and (iii) we refine the head on whole passages using the
noisy per-atom labels produced by atomic-fact verification as auxiliary
supervision, so the head learns to rank uncertainty \emph{across} the
atoms in a response rather than scoring each atom in isolation. This
yields a scalable framework for real-time activation-based uncertainty
detection in long-form LLM generation.
\end{abstract}
