\section{Introduction}
Despite their remarkable performance across a wide range of tasks, the inner workings of Large
Language Models (LLMs) remain poorly understood. This lack of transparency is particularly
problematic in high-stakes scenarios, where LLMs are prone to ``hallucinations'' -- cases in which the
model generates false or fabricated content \citep{smtonmoy2024,liu2021,huang2023,ji2023,vipularawte2023}. Accurate Hallucination Detection
(HD) is critical for the safe and reliable deployment of LLMs \citep{qiu2023,li2023,sahoo2024}. While existing methods
for detecting such hallucinations often rely on auxiliary LLMs or repeated prompting \citep{kuhn2023,orgad2024},
these approaches tend to be slow and computationally intensive (up to several seconds per instance \citep{barshalom2025}).
A prominent class of methods suggest to overcome this additional computational cost via probing
classifiers: simple models trained on internal LLM representations to predict certain attributes \citep{belinkov2022}.
These techniques have been central to interpretability research \citep{gupta2015a,kohn2015,shi2016a,ettinger2016,adi2016,conneau2018a,belinkov2019}, with linear
probes gaining popularity for their transparency and simplicity \citep{alain2018,hupkes2018,nelsonfliu2019,hallmaudslay2020,orgad2024}.

Unfortunately, traditional probing classifiers exhibit two fundamental limitations. First, they operate
on isolated layer--token pairs, neglecting information from other activations within the model. This is
critical: while predictive hallucination signals might indeed appear at specific ``exact tokens'', their positions vary across responses, making the position-finding a difficult problem on its own---practically
requiring (multiple) LLM queries \citep{orgad2024}. In addition to this, these signals may also peak at different
layers on a per-dataset basis \citep{azaria2023}, underscoring the need for a more holistic processing of the model's
internal state. A second limitation is that probing classifiers are model-specific, thus unable to generalize across LLMs or to benefit from hallucination-related insights found in other LLMs. This hinders
sharing datasets across LLMs, transfer learning, and multi-model training. Crucially, each new
LLM or text generation task demands annotating a new dataset, a tricky and sometimes impractical
procedure. Motivated by the above, we ask: (i) Can we design an architecture that processes the full
internal state of an LLM and benefit from it?; and (ii) Can it learn across multiple LLMs and benefit
from it? In this paper, we positively answer these questions and propose a novel approach, dubbed
ACT-ViT, addressing the aforementioned limitations in an effective and efficient way.

\input{figs/fig1_overview}

We start by providing further evidence on the limitations of single-position, static probing classifiers.
On top of previous observations suggesting that the best probe-position varies across tokens and
layers on a per-sample and dataset basis \citep{orgad2024,azaria2023}, we show that the location of predictive signals for
hallucinations also widely varies across LLMs, even for the same dataset. This further calls for
the development of a more sophisticated approach that can adaptively attend to the most predictive
``locations'' within models' hidden states, especially if aiming to operate beyond the single-LLM
regime. To this end, we propose leveraging, as our basic data type, what we term the Activation
Tensor (AT) -- a comprehensive representation of the LLM's internal state with respect to a given
input. Formally, for an LLM $M$ and a $N$-long response to some input query, the AT is denoted
$A \in \mathbb{R}^{L_M \times N \times D_M}$, with $L_M$ the number of layers, $D_M$ $M$'s hidden dimension. ATs are informative
but challenging to process: they are large, high-dimensional, and LLM-dependent. We process them
efficiently and effectively by exploiting their structural similarity to images. An RGB image forms a
$H \times W \times 3$ tensor with spatial dimensions (a grid of pixels) and feature channels. Similarly, Activation
Tensors have ``spatial'' dimensions described by layer stacks ($L_M$) and token sequences ($N$), and a
feature dimension corresponding to the dimensions of the LLM's hidden states. This analogy enables
applying proven computer vision techniques like spatial pooling and Vision Transformers \citep{dosovitskiy2020}.

To unify ATs across different LLMs into a consistent shape, we apply pooling over the spatial
dimensions, followed by an LLM-specific Linear Adapter (LA) on the feature dimension. This
transforms all tensors into a shared shape of $L_p \times N_p \times D'$. The resulting representation is then fed
into a shared ViT-based backbone. See Figure~\ref{fig:overview} for a complete depiction of our framework. These
components are jointly trained for HD on multiple annotated AT datasets originating from different
LLMs. Importantly, our use of linear adapters is inspired by recent work \citep{huh2024,moschella2022} suggesting that
LLMs converge towards a shared statistical model of reality, with the notion of universal truthfulness
\citep{marks2023,slobodkin2023} positing they learn a generalizable, linearly exploitable representation of factual truth. A key
aspect of our architecture is its ability to be applied to new, unseen LLMs. In these cases, it suffices
to only train the lightweight, LLM-specific LA, while the backbone -- pretrained for HD in a unified
representation space across LLMs -- is kept frozen.

\paragraph{Results.} In our extensive experiments across 15 LLM--dataset combinations, ACT-ViT consistently
outperforms traditional probing methods in both single- and multi-LLM training settings. Remarkably,
it exhibits strong zero-shot generalization to new datasets from LLMs seen during training and
requires as little as $\approx 5\%$ of the training data to improve performance further and -- in many cases --
surpass traditional probes trained on the whole dataset. Furthermore, by training only the lightweight
LA for a new unseen LLM, our model achieves superior performance than standard probes. ACT-ViT
trains on a single GPU in less than three hours on all 15 LLM-dataset combinations together, and
detects hallucination in less than $\approx 10^{-5}$ seconds per instance at inference time.

\paragraph{Contributions.} (1) We propose Activation Tensors (ATs) as a holistic, structured representation of
LLM internals. (2) Inspired by the similarity of ATs to images we introduce a novel architecture that
can effectively train on ATs from multiple LLMs and datasets. We show it outperforms traditional
probes, even when trained only on a single LLM. (3) We demonstrate strong transfer capabilities:
zero-shot generalization to new datasets on LLMs that were seen during training, and fast adaptation
to out-of-domain LLMs with only a newly trained linear adapter, keeping the remaining parameters
frozen. (4) We show our method is highly efficient during both training and inference.
