\section{Towards Weakly Supervised Temporal Uncertainty Localization}
\label{sec:non_static}

Mechanistic detectors face a tension between coverage and scalability.
Static probing classifiers \citep{azaria2023,orgad2024} operate on a
single layer-token position and ignore signal elsewhere in $A$; the
optimal position varies across samples, datasets, and LLMs, often
requiring an external search \citep{orgad2024}. Methods that consume
the full hidden-state activations capture distributed signal but are
ill-suited to real-time long-form generation: activation-map probes
face a speed--accuracy tradeoff, where keeping the map small and
pooled loses accuracy as responses grow long, while scaling the map
up sacrifices inference speed by requiring one forward per token.
Even when an activation-map method does scale, a single
sequence-level score does not say where the suspicious activations
lie, a poor fit for responses where most tokens are correct and only
a few are problematic.

\paragraph{Activation-map probes do not scale to long responses.}
Appendix Figure~\ref{fig:perf_by_length} reports per-token AUROC on
LongFact as the input prefix length $T$ grows, and makes the
speed--accuracy tradeoff concrete. ACT-ViT with a short pooled
token axis is cheap but performs well only on short prefixes; its
accuracy drops as more generated tokens are compressed into the
same fixed-size representation. Widening the pooled axis partially
reduces this collapse at the cost of inference speed, but still
does not recover Temp-ViT's flatter performance across response
lengths. This supports our central design choice: instead of
compressing the whole response's activation map into one fixed-size
representation, Temp-ViT scores local token windows and models their temporal
evolution.

\paragraph{Why windows instead of isolated tokens?} Hallucination
labels are usually available at the sequence, sentence, or claim level,
not at the token level. Moreover, the activation signal
is not confined to the hallucinated token itself.
Figure~\ref{fig:signal_propagation} measures this directly: on
RAGTruth, a linear probe's ROC-AUC ramps from chance at offset $-24$
to $0.66$ at the token immediately before a hallucinated span, rises
monotonically through the span ($0.71 \to 0.79$), and decays slowly
afterward. Adjacent context therefore carries useful uncertainty
signal, while direct token supervision would be noisy. We treat span
labels as weak supervision and learn to localize uncertainty through
window-level temporal modeling.

\input{figs/fig_signal_propagation}
\input{figs/fig1_overview}

\paragraph{Why encode activations as 2D images?}
Per layer and token probes show that the useful hidden state signal is not concentrated
in one fixed position. Instead, informative regions appear across both the layer direction 
and the token direction, and the most predictive regions change from one LLM to another, 
as shown by the heatmaps in Appendix~\ref{app:heatmaps}. This means that layers and tokens 
form a connected spatial pattern, rather than two independent axes that can be reduced separately. 
A probe that reads only one layer and token or splices them can discard part of this pattern.
ACT ViT \citep{barshalom2025actvit} supports this view by treating the layer by token activation plane
as an image and showing that a vision encoder over this plane performs better than the strongest single
position probe across models and datasets. This suggests that joint image style processing preserves predictive
signal that would otherwise be lost, motivating an encoder that reads the full layer and token plane
instead of relying on a single fixed hidden state slice.

\paragraph{Weakly supervised temporal localization.} ACT-ViT shows
that the $(L,T)$ plane has spatial structure amenable to visual
encoders, but a single fixed-size image fits poorly when $T$ ranges
from a handful to thousands of tokens. We frame $A$ as a video
over the token axis and borrow WSTL from video understanding
\citep{pilhyeonlee2021}. Each token is a frame whose height is the
layer axis and whose channels are the hidden dimension; a
window aggregates $W$ consecutive tokens. The neighbourhood
structure of Figure~\ref{fig:signal_propagation} is exactly what a
window exploits: surrounding tokens emit usable signal about whether
a target token is hallucinated, so the model can localize spans of
uncertainty without window-level labels.

\paragraph{Three-stage training.} Learning sequence-level uncertainty
and window-level localization jointly under weak supervision is a
hard optimization. We decompose training into three stages.
Stage 1 trains the encoder on full hidden-state activations with
sequence-level labels. Stage 2 fine-tunes the encoder jointly with
a temporal head \citep{albertgu2024} over per-window encodings via
top-$k$ MIL against the same sequence label, so the head learns to
localize the uncertainty signal to a few windows inside each claim
without per-window supervision.
Stage 3 trains the head across claims in the full sequence:
fine-tuning on whole passages with per-claim auxiliary labels
teaches it how the uncertainty activation signal changes across
claims, in particular on mixed-content windows whose receptive
field contains both hallucinated and supported tokens (which
Stages~1 and 2 never see). We describe each stage in the next section.
