\section{Method}
\label{sec:model}

Figure~\ref{fig:overview} illustrates the three-stage pipeline.
Stage~1 trains a sequence encoder $E_\theta$ that maps the full
hidden-state activations $A \in \mathbb{R}^{L \times T \times D}$ to
a sequence-level logit. Stage~2 fine-tunes $E_\theta$ jointly with a
Mamba-2 temporal head \citep{albertgu2024} on centered length-$W$
token windows $\{A^{(t)}\}_{t=1}^{T}$; the head emits one logit
$\hat{z}^{(t)}$ per window. Stage~3 freezes the encoder,
initializes the head from Stage~2, and refines it on whole passages
under per-claim auxiliary supervision.

\subsection{Problem setup and notation}
\label{sec:notation}

Given an LLM $M$ and its generated response of length $T$, we
collect the hidden-state activations
$A \in \mathbb{R}^{L \times T \times D}$
($L$ transformer layers, $D$ hidden dimension). For temporal
localization we additionally use the windowed view
$A^{(t)} \in \mathbb{R}^{L \times W \times D}$ obtained by slicing
$A$ over $W$ consecutive tokens centered at $t$. Training data
comes with a sequence-level label $y \in \{0,1\}$ (hallucinated
vs.\ not), and on long-form corpora with noisy per-claim auxiliary
labels $\{(\ell_m, r_m, \tilde{y}_m)\}_{m=1}^{M}$ from claim-level
verification, where each claim $m$ is identified with its token
span $(\ell_m, r_m)$ so we refer to a claim and its span
interchangeably. Given $A$, our goal is to predict both a
sequence-level uncertainty score $\hat{p} \in [0,1]$ and per-window
scores $\{\hat{p}^{(t)}\}_{t=1}^{T}$ under this weak supervision;
the full notation, dataset construction, white-box assumptions, and
off-domain generalization scenarios are deferred to
Appendix~\ref{app:extended}.

\subsection{Stage 1: Encoder}
\label{sec:act_vit_subsec}

The encoder has three components. Pool applies adaptive
max-pooling over $(L, T)$ to a target spatial size $(L_p, T_p)$,
yielding $A_p \in \mathbb{R}^{L_p \times T_p \times D}$. LA
is a per-LLM linear adapter $LA_M : \mathbb{R}^D \to \mathbb{R}^{D'}$
that aligns hidden dimensions across models in $\mathcal{M}$:
\begin{equation}
\mathcal{L} = \{ LA_M \mid M \in \mathcal{M},\ W_M \in \mathbb{R}^{D_M \times D'} \},
\end{equation}
motivated by recent evidence that LLM representations can be put in
approximate correspondence by linear maps
\citep{huh2024,moschella2022,kornblith2019}. ViT-B treats the
$(L_p \times T_p)$ plane as an image, splits it into non-overlapping
$(p_H, p_W)$ patches, adds learnable intra-patch positional encodings,
and processes the patch sequence with a Transformer. A linear head
emits the Stage-1 logit $z$, trained with
$\mathcal{L}_{1} = \mathrm{BCE}(\sigma(z), y)$ where $y$ is the
sequence label. The features before the linear head form the
per-sequence embedding that Stages 2 and 3 reuse.

\subsection{Stage 2: Temporal Localization with Top-$k$ MIL}
\label{sec:temporal_head}

For each generated position $t$, we extract the windowed activations
$A^{(t)} \in \mathbb{R}^{L \times W \times D}$ as $W$ token
columns of $A$ centered at $t$ (edge-padded near response boundaries).
The same Pool is reused with a smaller token target
$(L_p, W_p)$ and $E_\theta$ produces a per-window embedding
$e^{(t)} \in \mathbb{R}^{d}$. Stacking the $T$ windows yields
$E \in \mathbb{R}^{T \times d}$. A residual stack of Mamba-2 blocks
processes $E$ along the token axis followed by a linear head:
$\hat{z}^{(t)} = h(\mathrm{Mamba\text{-}2}(E)_t)$.
Mamba-2's linear-time selective state-space recurrence makes Stage 2
viable for real-time streaming, where each new token requires only a
constant-memory update.

Because only sequence-level labels are
available, we train via top-$k$ MIL: after masking padded positions,
take the $k$ largest per-window logits and average them into one
sequence-level logit:
\begin{equation}
\hat{z} = \tfrac{1}{k}\!\!\!\sum_{t \in \mathrm{Top}_k(\{\hat{z}^{(t)}\}_t)}\!\!\!\hat{z}^{(t)}, \qquad \hat{p} = \sigma(\hat{z}),
\end{equation}
and supervise with $\mathcal{L}_{2} = \mathrm{BCE}(\hat{p}, y)$.
Mean-of-top-$k$ is more stable than max (brittle to single outliers)
or full mean (dilutes signal in mostly-correct responses), and lets
the model localize the uncertainty signal to a few windows inside
each span without window-level labels.

\subsection{Stage 3: Cross-Claim Refinement}
\label{sec:stage3}

Stages 1 and 2 see one claim segment at a time and never observe how the
uncertainty activation signal changes across a claim. In
particular, mixed-content windows (windows whose receptive field
straddles both hallucinated and supported tokens) combine two signal
regimes that single-claim training cannot disentangle. Stage 3 fixes
this by training the head across spans in the full sequence rather
than on isolated claim segments: with the encoder frozen, the head is
fine-tuned on whole passages with per-claim auxiliary labels so it
learns the spatial profile of the signal within and across claims.

Stage 3 takes as input passage-level activations
$A \in \mathbb{R}^{L \times T \times D}$ paired with $M$ claims
$\{(\ell_m, r_m)\}_{m=1}^{M}$ and noisy labels
$\tilde{y}_m \in \{0,1\}$ from claim-level verification.

The Stage-2 detector emits per-token logits
$\hat{z}^{(1)}, \ldots, \hat{z}^{(T)}$ over the passage. We smooth
them along the token axis with a centered length-$W$ softmax-weighted
window,
\begin{equation}
\bar{z}^{(t)} = \!\!\!\!\!\sum_{u \in \mathcal{W}(t)}\!\!\!\! \alpha_u^{(t)}\, \hat{z}^{(u)},\qquad \alpha_u^{(t)} \propto \exp(\hat{z}^{(u)}/\tau),
\end{equation}
where $\tau \to 0$ recovers max and $\tau \to \infty$ recovers mean.
The per-claim logit is a top-$k$ mean over the smoothed logits in the
claim,
\begin{equation}
\hat{z}_m = \frac{1}{k_m}\!\!\!\sum_{t \in \mathrm{Top}_{k_m}(\mathcal{S}_m)}\!\!\! \bar{z}^{(t)},
\end{equation}
where $\mathcal{S}_m = \{\bar{z}^{(t)}\}_{t=\ell_m}^{r_m}$ are the
in-span smoothed logits and
$k_m = \max(k_{\min}, \lceil \kappa\,(r_m - \ell_m + 1) \rceil)$ with
$\kappa \in (0, 1]$. The Stage-3 loss is a per-claim BCE,
$\mathcal{L}_{3} = \tfrac{1}{|\mathrm{valid}|}\sum_m \mathrm{BCE}(\sigma(\hat{z}_m), \tilde{y}_m)$,
which forces the head to learn how the per-token signal varies within
and across claims, including on mixed-content windows, rather
than score each claim in isolation.

At inference time, a single forward through the Stage-3 detector
yields the per-token logits over the whole passage, from which we
read off (i) the per-token / per-window scores
$\{\sigma(\hat{z}^{(t)})\}_{t=1}^{T}$ for token-level localization;
(ii) per-sentence scores obtained by aggregating the smoothed
per-token logits within each sentence span with the same top-$k$
mean; (iii) per-claim scores $\{\sigma(\hat{z}_m)\}_m$ when claims
are available; and (iv) a sequence-level score by reusing the
Stage-2 top-$k$ MIL aggregation.
