\section{Experiments}
\label{sec:experiments}

\paragraph{Setup.} We experimentally analyze various aspects of learning on ATs with ACT-ViT. We consider,
in particular, two relevant setups: (a) in-domain and (b) out-of-domain.

The in-domain setup (a) is the setting commonly considered in HD literature: it assesses the generalization performance on data from a known LLM on known generative tasks, i.e., it assumes
training-time access to annotated data for a target LLM and task of interest. In this standard scenario, we attempt answering the following questions: (Q\textsubscript{1}\textsuperscript{(a)}) Does our method outperform standard
methods, including probing classifiers? (Q\textsubscript{2}\textsuperscript{(a)}) What is the contribution of multi-dataset training?
(Q\textsubscript{3}\textsuperscript{(a)}) Is the vision architectural inductive bias effective? (Q\textsubscript{4}\textsuperscript{(a)}) How scalable is our approach?

Harder -- but more compelling -- is the out-of-domain setup
(b). Here, we benchmark methods in cases where either
the target dataset is unseen at training time, or, even more
challenging, both the target dataset and the target LLM
are unseen. We study, in particular, the performance of
our approach when either no data or only a small amount
is available for adaptation. Those correspond, resp., to
zero-shot generalization, and to fine-tuning only the LA
in our pipeline, keeping the other parameters frozen (see
inset). These settings reflect relevant real-world use-cases
pertaining to, e.g., newly introduced LLMs and/or generative tasks with hardly accessible hallucination labels. Our experiments revolve around the following questions: (Q\textsubscript{1}\textsuperscript{(b)}) Can our method
effectively generalize on unseen datasets? Does it adapt in a sample-efficient manner? (Q\textsubscript{2}\textsuperscript{(b)}) Can it
handle unseen LLMs by only training the corresponding Linear Adapters? (Q\textsubscript{3}\textsuperscript{(b)}) Does this approach
favorably compare with baselines?

\paragraph{LLMs and datasets.} Aligning with prior work, we focus on the datasets and LLMs considered
in \citep{orgad2024,barshalom2025}. We experiment with Mistral-7B-Instruct-v0.2 \citep{albertqjiang2023} (Mis-7B) and Llama-3-8B-Instruct
\citep{touvron2023} (LlaMa-8B) over the generation tasks encompassed by the following datasets: TriviaQA \citep{joshi2017}
(question answering), HotpotQA with (HQA-Wc) and without supporting context (HQA) \citep{yang2018}
(question answering), IMDB movie review \citep{maas2011} (sentiment analysis), and Movies \citep{orgad2024} (actor role
retrieval). On top of this, we additionally include another LLM: Qwen2.5-7B-Instruct \citep{yang2024} (Qwen-7B). This setup yields a total of 15 distinct LLM-dataset combinations. We use the area under the
ROC curve (AUC) to evaluate error detectors, a standard metric in this domain \citep{orgad2024,snyder2024,barshalom2025}.

\paragraph{Methods in comparison.} We compare the performance of a diverse set of methods: (1) Probabilities/logits-based. To detect errors, several works \citep{nunomguerreiro2022,kadavath2022,varshney2023,huang2023a} assess LLM confidence by
aggregating output token probabilities or logits by taking the mean, max, or min across these scores.
We refer to these with the naming Logit/Probas-mean/min/max. These approaches operate in a
less-restrictive setting, and thus constitute important baselines for our method. They are especially
relevant in the out-of-domain setup (b), since, being training-free, these methods are (degenerately)
sample-efficient by construction. We also compare against LOS-Net \citep{barshalom2025}, a recent, learnable approach on output probabilities. (2) Probing Classifiers \citep{belinkov2022} constitute natural and effective white-box
baselines for our approach \citep{kadavath2022,li2024}. For each benchmark, we learn logistic regression probes on
each layer of the LLM and across a fixed set of token positions $\mathcal{N}$ (see Section~\ref{sec:non_static}), a superset of the
top-performing (static) tokens identified in \citep{orgad2024}. The best layer-token combination, as well as the
$L_2$ regularization coefficient, is selected on the respective validation sets. We refer to this method
as Probe[$*$]. With Token[$n$], $n \in \mathcal{N}$, we refer, instead, to the probe specific to token position
$n$. (3) Activation Tensors-Methods are those designed and introduced in this work. ACT-ViT,
(Section~\ref{sec:act_vit_subsec}) is trained on the corpus of all available training sets across LLMs and datasets. In the
out-of-domain setup (b), some of these are purposely segregated from the corpus in an effort to study
domain adaptation abilities; this will be appropriately specified. We also benchmark two variants
of our approach to separately study the benefits of multi-dataset training and architectural inductive
biases. We use ACT-ViT(s) to refer to the single LLM-dataset counterpart of our method trained
individually on each of the 15 LLM--dataset combinations. ACT-MLP and ACT-MLP(s) denote, instead,
simplified variants in which MLPs operate on the output of Pool, flattened. These are trained, resp.,
on the full training corpus\footnote{With appropriate padding to $D_{\max}$ -- the largest hidden size among the considered LLMs} or separately on each single training set. Across all these architectures, if
not specified otherwise, we use the fixed pooling hyperparameter of $(L_p, N_p) = (8, 100)$.

Next we present our main results, with additional experimental details and experiments in Appendix~\ref{app:extended}.
