\section{Results}
\label{sec:results}

\subsection{Temp-ViT improves token-level hallucination
localization}
\label{sec:results_token}

The headline contribution is per-token localization on long-form
text. Table~\ref{tab:main} reports token-level AUROC on RAGTruth
\citep{niu2024ragtruth}, FactScore \citep{min2023}, and LongFact
\citep{wei2024} for two LLMs. On every populated cell, the
Temp-ViT family beats both the Confidence baselines (which top out
near 0.60) and the strongest mechanistic baseline (Act-ViT
\citep{barshalom2025}, the pooled-tensor sequence encoder we build
on). On RAGTruth the gap is largest -- Encoder Only + PRR reaches
$0.888^\dagger$ on Mis-7B-Inst and $0.846$ on LlaMa-13B-Inst,
against $\leq 0.615$ for every non-Ours row. On FactScore /
LongFact the gap narrows but the ranking is preserved.

The two Ours variants split the column lead: Encoder Only + PRR
wins token-level on Mis-7B-Inst (all three datasets) and on
LlaMa-13B-Inst (FactScore, LongFact), while Temp-ViT + PRR wins
the LlaMa-13B-Inst RAGTruth cell. The pattern answers
(Q\textsubscript{1}): Confidence and Mechanistic baselines are
near chance at the token level on these corpora; the supervised
window encoder is what lets the score localize within a passage.

\subsection{Gains persist at sentence and claim level}
\label{sec:results_aggregated}

\input{figs/tab3_sentence}
\input{figs/tab4_claim}

Per-token scores aggregate upward without retraining.
Table~\ref{tab:sentence} reports sentence-level verdicts under
AND-on-supported aggregation (any unsupported claim in a sentence
flips the sentence to hallucinated; score is the max per-token
uncertainty in the span). Table~\ref{tab:claim} reports claim-level
verdicts (one row per claim from the sidecar).

At both granularities the Ours rows dominate every populated cell
except FactScore / LongFact for LlaMa-13B-Inst, where MeanTokenEntropy
edges out by 1--3 AUROC points. RAGTruth shows the cleanest
separation: Temp-ViT + PRR reaches $0.929$ sentence AUROC on
LlaMa-13B-Inst against the next-best baseline at $0.657$. The
gap widens as granularity narrows from sentence to claim, which
is the regime where the per-token head must rank claims against
each other within the same passage. Sentence-length distributions
that determine which granularity is feasible to supervise are
reported in Table~\ref{tab:long_form_stats}; LongFact and
FactScore claims are typically much shorter than RAGTruth's,
which the per-token head benefits from at sentence and claim
levels.
