\subsection{TPE outperforms baselines in uncertainty
quantification}
\label{sec:results_polygraph}

\input{figs/tab2_ood}

The LM-Polygraph benchmark
\citep{fadeeva2023lmpolygraph,vashurin2025lmpolygraph} stresses
the sequence-level use case: each test item is a short- or long-form
response and the goal is to rank responses by likely hallucination,
not to localize within them. Table~\ref{tab:polygraph} reports
per-category PRR on three capability categories of LM-Polygraph,
aggregated across the datasets present in each category for
Mis-7B-Inst: \emph{QA} (TriviaQA, CoQA, MMLU; today only MMLU
is filled), \emph{CoT} (GSM8k), and \emph{NMT} (WMT14, WMT19;
today only WMT19 is filled). The disaggregated per-dataset values
are reported in the ablation
Table~\ref{tab:polygraph_extended}. The Encoder Only row
aggregates per-window logits to a single number per response via
top-$k$ MIL, matching the training-time aggregator
(Section~\ref{sec:temporal_head}); the full TPE row uses the
Stage~3 passage-level head.

Encoder Only wins NMT ($0.816$) and slightly edges the Act-ViT
mechanistic baseline on QA ($0.114$ vs $0.113$). The full TPE
row loses some accuracy on the QA category: its Stage~3
objective is trained on long-form passages with many claims, and
the per-claim loss does not transfer back to single-claim
sequences as cleanly as the Stage~2 MIL objective. This is the
secondary contribution; the primary use case is localization
(Sections~\ref{sec:results_token}, \ref{sec:results_aggregated}),
but the per-token detector remains competitive as a sequence-level
ranker. Per-dataset sequence-length distributions are in
Table~\ref{tab:polygraph_stats}.

\subsection{Efficiency analysis}
\label{sec:results_efficiency}

TPE scores every generated token in a single forward through
the frozen encoder and the temporal head, so the cost of obtaining
sentence-level scores is amortized across the passage
rather than scaling with the number of claims.
Figure~\ref{fig:inference_time} quantifies this on a $T = 384$
LongFact passage: $25\times$ wall-clock advantage over
sequence-level pooled-activation baselines that must be re-invoked
per claim. Training the passage-level
refinement stage takes under three hours on a single H200 across
all three LLMs. Aggressive pooling
($(L_p, N_p) = (4, 20)$) preserves most of the downstream AUROC
while shrinking training to a few minutes.

\input{figs/fig_inference_time}
