\subsection{Off-domain Hallucination Detection}

\paragraph{Hallucination Detection on unseen datasets.} We implement a ``leave-one-dataset-out'' setup: for
each LLM-dataset pairing, we train ACT-ViT on the corpus of the remaining 14 out of 15 combinations, and then evaluate on the target held-out test set zero-shot\footnote{On held-out LLM-data pair $(M, D)$, this is possible as $M$'s LA is pretrained on the pairs $(M, D')$, $D' \neq D$.}. This is something fundamentally
not possible with standard probing methods and hence compare against the best probability-based
baseline, denoted Best-Probas, due to its training-free nature, and against ACT-MLP.

Results are shown as bar plots in Figure~\ref{fig:zeroshot} on all 15 LLM--dataset combinations. We observe strong
generalization performance: ACT-ViT outperforms Best-Probas in 13 out of 15 cases, sometimes
substantially. On the IMDB dataset with Mis-7B, ACT-ViT achieves a gain of $+37$ AUC points.
ACT-MLP also shows reasonable performance, but it consistently falls short of ACT-ViT. These results
provide a positive answer to (Q\textsubscript{1}\textsuperscript{(b)}).

\input{figs/fig4_zeroshot}

We next consider a more tolerant setting whereby only
a limited amount of samples from the target training
set is available. In particular, we start with the pre-trained ACT-ViT and fine-tune the LA module keeping
the ViT-B component frozen. We compare with Best-Probas and Probe[$*$], fitted only the corresponding available training data. Figure~\ref{fig:lowdata} shows Test AUCs for Mis-7B
over HotpotQA across varying fine-tuning set sizes; results for other 15 LLM-dataset combinations are in Appendix~\ref{app:lowdata}. ACT-ViT consistently outperforms all baselines across all training fractions. Importantly, the performance gap between ACT-ViT and Probe[$*$] widens as the
training set shrinks, indicating that the frozen ViT-B backbone captures strong, transferable features learned from
(pre)training on other LLMs and datasets. Additionally,
ACT-ViT requires only 10\% of the available training data
(1k samples) to surpass Probe[$*$] when trained on the full 10k-sized training set.

\input{figs/fig5_lowdata}

\paragraph{Hallucination Detection on unseen LLMs and datasets.} We finally benchmark our method in
the following challenging setup: we train ACT-ViT on 2 out of 3 LLMs and leave the third one out.
Specifically, our model is pretrained on a corpus of 10 out of 15 training sets containing no data
from target LLM $M$. It is then (separately) adapted on the remaining 5 datasets by keeping ViT-B
frozen and only training the LA\textsubscript{$M$} module from scratch. In Table~\ref{tab:ood} we report the obtained Test
AUCs, comparing ACT-ViT against Best-Probas and Probe[$*$]. ACT-ViT outperforms these baselines
in 13 out of 15 cases. Recalling that the ViT-B module is frozen during adaptation, this further
demonstrates how the features learned during (pre)training over different LLMs can strongly transfer
to an unseen one. Along with the above, these results answer positively to Q\textsubscript{2}\textsuperscript{(b)} and Q\textsubscript{3}\textsuperscript{(b)}.

\input{figs/tab2_ood}
