\section{Ablations}
\label{sec:ablations}

\paragraph{Architecture variants (Table~\ref{tab:window_ablation}).}
We compare the full TPE pipeline against an MLP-encoder baseline
(no windowing) and an encoder-only variant (no temporal head), across
the three stages. The encoder-only Stage~3 variant matches or beats
the full pipeline on AUROC on both RAGTruth cells, indicating that
the encoder's windowed pooling absorbs most of the local-context
signal; the temporal head's contribution comes from sequence-level
aggregation.

\paragraph{Stride (Table~\ref{tab:stride}).} We sweep the window
stride from 1 (the default, one window per token) to 4, 6, and
``no overlap'' (stride $=$ window size). Larger strides reduce
inference cost at the price of resolution.

\paragraph{Stages (Table~\ref{tab:stage}).} AUROC and PRR improve
monotonically from Stage 1 to Stage 3, with Stage 3 delivering the
largest gain on Llama-2-13b. The full per-stage table is provided on
two RAGTruth cells where stage-by-stage caches were available;
LlaMa-70B-Inst stage sweeps are pending.

\paragraph{Dataset statistics
(Tables~\ref{tab:long_form_stats},~\ref{tab:polygraph_stats}).}
Passage- and claim-length distributions help interpret which
granularities are feasible to supervise: LongFact and FactScore claims
are typically much shorter than RAGTruth's, which the per-token head
benefits from at the sentence level.

\paragraph{Per-dataset LM-Polygraph results (Table~\ref{tab:polygraph_extended}).}
The main-paper Table~\ref{tab:polygraph} reports per-category PRR
aggregates (\emph{QA}, \emph{CoT}, \emph{NMT}).
Table~\ref{tab:polygraph_extended} disaggregates those aggregates back
to one column per dataset, so the contribution of each dataset to its
category mean is recoverable directly. Today only MMLU (QA), GSM8k
(CoT), and WMT19 (NMT) are populated on Mis-7B-Inst, so each
per-category aggregate is identical to its single underlying
per-dataset value; the extended table will become informative once
TriviaQA / CoQA / WMT14 cells are filled.

\paragraph{Calibration on LM-Polygraph (Table~\ref{tab:polygraph_ece}).}
Table~\ref{tab:polygraph} compares uncertainty scores by ranking quality
(PRR); Table~\ref{tab:polygraph_ece} reports calibration via Expected
Calibration Error on the same three Mis-7B-Inst cells. Lower ECE is
better. Act-ViT and Encoder~Only are the best-calibrated detectors on
MMLU (ECE $\leq 0.064$, vs. $> 0.5$ for most Confidence baselines);
TPE wins the calibration race on GSM8k ($0.066$). The picture on
WMT19 differs: short, well-conditioned Confidence baselines
(TokenSAR, MeanTokenEntropy, Perplexity) are already well-calibrated on
NMT outputs, so the supervised detectors trail them on ECE while still
winning the PRR ranking comparison. Ranking quality and calibration are
orthogonal --- this table makes that explicit.

\paragraph{In-distribution vs out-of-distribution (Table~\ref{tab:ood}).}
RAGTruth contains three task types: QA, summarization, and data-to-text.
We train two versions of TPE and evaluate both on the data-to-text
subset: a \emph{baseline} trained on all three task types, and an
\emph{OOD} variant trained only on QA and summarization. The gap
between the two rows measures how much of the per-token detector's
performance on data-to-text is attributable to in-domain supervision
versus transferable activation signal from the other task types.

\paragraph{Token-level overlap resolution.}
\label{ablation:overlap_rule}
The token-level eval (Table~\ref{tab:main}) derives each generated
token's label from the per-claim span labels
$(\ell_m, r_m, \tilde{y}_m)$. Spans are sorted by
$(\ell_m\!\uparrow, r_m\!\downarrow)$ -- earlier start first, longer
span first on a tie -- and walked in order; each span writes its
label $1-\tilde{y}_m$ to every still-uncovered token in
$[\ell_m, r_m\!+\!1)$. Tokens that no span covers are then dropped
from the eval pool. Concretely: on partial overlap the earlier-starting
span wins; on containment with a common start the longer (outer)
span wins; on containment with a later inner start the outer span
still wins, because it claims the shared tokens first. The inner
span only contributes the tokens the outer one does not cover.
This matches the non-overlap training deduplication rule on the
strict common-start case, and diverges only when the inner span
starts later, where the earlier-start tiebreak is equivalent to a
longer-span tiebreak in practice because the outer is necessarily
$\geq$ as long.

\paragraph{Full activation coverage and long-form scaling.}\label{app:full_activation_coverage}
ACT-ViT shows that layer-token activation structure is predictive, but
full-response pooling is the wrong inference unit for long-form
localization. Figure~\ref{fig:perf_by_length} reports per-token AUROC
on LongFact as the input prefix length $T$ grows: ACT-ViT with a short
pooled token axis is fast but loses accuracy as more generated tokens
are compressed into the same representation. Widening the pooled axis
partially reduces this collapse at the cost of inference speed, and
Figure~\ref{fig:inference_time} shows the runtime penalty when a
full-response activation map is rescored at each token. TPE instead
scores local token windows and models their temporal evolution,
avoiding one pooled representation for the whole response.

\input{figs/fig_perf_by_length}
\input{figs/fig_signal_propagation}
\input{figs/tab5_window_ablation}
\input{figs/tab6_stride_ablation}
\input{figs/tab7_stage_ablation}
\input{figs/tab8_long_form_dataset_stats}
\input{figs/tab9_polygraph_dataset_stats}
\input{figs/tab10_ood_ablation}
\input{figs/tab12_polygraph_ece}
\input{figs/tab13_polygraph_extended}
