\section{Extended Experimental Section}
\label{app:extended}

\paragraph{Problem setting.} Given an LLM $M$, an input query $\vec{s}$, and the model-generated response $\vec{\hat{g}}$ of length $T$, our goal is twofold: (i) predict whether $\vec{\hat{g}}$ is hallucinated, and (ii) localize which generated-token regions show uncertainty signals in the hidden-state activations. We assume a white-box setting (full access to internal states of $M$) and disallow external resources such as auxiliary LLMs, retrieval, or repeated sampling, so detection can run alongside generation in real time.

\paragraph{Token windows.} For temporal localization, we consider local views of $A$ along the token axis. For a window size $W$ and a position $t \in \{1, \dots, T\}$, the windowed activations $A^{(t)} \in \mathbb{R}^{L \times W \times D}$ are obtained by slicing $A$ over $W$ consecutive tokens centered at $t$, with edge padding when $t$ is near a response boundary. The full response is then covered by the sequence $\{A^{(t)}\}_{t=1}^{T}$ of overlapping windows, each providing a local view of the activation patterns associated with a short generated-token region.

\paragraph{Dataset construction.} Following \citet{orgad2024}, we consider datasets $\mathcal{D} = \{(\vec{s}_i, \vec{g}_i)\}_{i=1}^m$ of question-answer pairs, e.g., (``Who developed the theory of general relativity?'', ``Albert Einstein''). For each query $\vec{s}_i$, the model produces a response $\vec{\hat{g}}_i$ from which we extract the hidden-state activations $A_i$. We assign a sequence-level binary hallucination label $y_i$ by comparing $\vec{\hat{g}}_i$ with $\vec{g}_i$, setting $y_i = 1$ when the response is incorrect/hallucinated and $y_i = 0$ otherwise. The final activation dataset is $\mathcal{A} = \{(A_i, y_i, M_i)\}_{i=1}^m$, where $M_i$ identifies the LLM that produced $A_i$, and multiple distinct $M_i$'s from a known collection $\mathcal{M}$ are allowed within the same dataset. Crucially, no clean token- or window-level labels are provided: the primary supervision signal is restricted to the sequence level. For long-form responses we additionally have access to a noisy auxiliary signal: a claim-level verification pipeline yields per-claim labels $\{(\ell_m, r_m, \tilde{y}_m)\}$ over $\vec{\hat{g}}_i$, where each claim $m$ is identified with its token span $(\ell_m, r_m)$ and $\tilde{y}_m \in \{0, 1\}$ is broadcast from the fact-level verification result. These per-claim labels are coarse (spans typically contain tokens that are not themselves hallucinated), so we treat them as auxiliary supervision rather than ground-truth window-level labels.

\paragraph{Problem statement and off-domain generalization.} We seek a parametric model that, given $A$, predicts (i) a sequence-level uncertainty score $\hat{p} \in [0, 1]$ and (ii) per-window uncertainty scores $\{\hat{p}^{(t)}\}_{t=1}^{T}$ that localize the generated-token regions whose activations most contribute to the sequence-level prediction. The sequence-level prediction is supervised directly by $y$; per-window scores must be learned under weak supervision from $y$ alone, and (on long-form corpora) from the noisy per-claim auxiliary labels $\tilde{y}_m$. Beyond the in-domain setting, we additionally consider (i) off-domain data generalization (activations are drawn from a known LLM $M \in \mathcal{M}$ but correspond to tasks or domains unseen during training) and (ii) off-domain model generalization (activations are drawn from a previously unseen LLM $M \notin \mathcal{M}$).

Our experiments use PyTorch \citep{paszke2019} on NVIDIA H200 GPUs. We
use the AdamW optimizer \citep{loshchilov2017} with a cosine learning
rate schedule and a 10\% warm-up phase. Hyperparameter tuning was
performed with Weights and Biases \citep{biewald2020}.

\paragraph{LLMs.} Three open-weight instruction-tuned models:
Mistral-7B-Instruct-v0.2 \citep{albertqjiang2023} (License:
Apache-2.0); Llama-2-13B-chat-hf \citep{touvron2023};
Llama-3.1-70B-Instruct \citep{touvron2023}. We access all three via
Hugging Face under their respective licenses.

\paragraph{Hidden-state activations.} Given an LLM $M$ and a response
of $N$ tokens, the hidden-state activations are
$A \in \mathbb{R}^{L_M \times N \times D_M}$ with $L_M$ layers and
$D_M$ hidden dimension. The $l$-th layer is the post-residual output
of the transformer block:
\begin{equation}
A^{(l)} = A^{(l-1)} + \mathrm{FFN}(\mathrm{Attn}(A^{(l-1)}; \theta_l^{\mathrm{attn}}); \theta_l^{\mathrm{ffn}}),
\label{eq:transformer}
\end{equation}
which we collect across all layers for every generated token.

\subsection{Layer-token probe heatmaps}
\label{app:heatmaps}

To diagnose where in the hidden-state activations the hallucination signal
lives, we follow \citet{orgad2024} on Mis-7B-Inst \citep{albertqjiang2023}
and train per layer-token logistic regression classifiers, restricting
tokens to $\mathcal{N} = \{0, 1, 2, -3, -2, -1\}$ (first and last three
positions). Figure~\ref{fig:heatmaps} reports ROC-AUC
heatmaps for three LLMs, with the best layer-token cell per LLM
boxed. Two patterns recur. First, predictive signal spreads across
many $(L, T)$ cells rather than concentrating at a single position,
so a probe that consumes only one cell discards most of the available
information. Second, the most informative position shifts across LLMs:
middle layers for Mis-7B-Inst and LlaMa-8B, late layers for Qwen-7B.
The best Mis-7B-Inst position, $(14, 0)$, transfers to LlaMa-8B and
Qwen-7B with $\approx 7\%$ AUC loss; no fixed slice suffices across
models. This motivates using an encoder over the full layer-token
plane rather than a single fixed hidden-state slice.

\input{figs/fig2_heatmaps}
