\subsection{Dataset Description}

In this section, we provide an overview of the five datasets used in our analysis; we mostly follow
the framework given in \citep{orgad2024} in constructing the datasets. We aimed to cover diverse tasks, reasoning
skills, and datasets, highlighting each one's unique value and how it complements the rest.

For all datasets, we used a consistent split of 10,000 training samples and 10,000 test samples, unless
otherwise specified. From the 10,000 training samples, 20\% (i.e., 2,000) were selected in a stratified
manner for validation, using a fixed random seed of 42.

\begin{enumerate}
\item HotpotQA with and without context (License: CC-BY-SA-4.0) \citep{yang2018}: HotpotQA is a
multi-hop question answering dataset featuring diverse questions that require reasoning
across multiple sources. Each instance includes supporting Wikipedia documents. We use
two settings in our analysis: (1) Without context, where questions are presented alone, testing
factual recall and reasoning; and (2) With context, where supporting documents are provided,
emphasizing the model's ability to leverage contextual information effectively.
\item Movies \citep{orgad2024} (License: MIT): We use this dataset to evaluate generalization in scenarios
regarding movies involving factual inaccuracies (i.e., hallucinations). This dataset contains
7857 test samples.
\item IMDB (originally released with no known license by \citet{maas2011}): This dataset consists
of movie reviews for sentiment classification. Following the method in \citep{orgad2024}, we employed a
one-shot prompt to help the large language model (LLM) apply the predefined sentiment
labels accurately.
\item TriviaQA (originally released with no known license by \citep{joshi2017}): A dataset of trivia question-answer pairs presented to the LLM without any supporting context, relying only on its
internal parametric knowledge. Multiple acceptable answer variants are provided to facilitate
automatic evaluation of response accuracy.
\end{enumerate}

\subsection{Additional Results}
\label{app:extra}

Below in Table~\ref{tab:losnet} we provide a comparison of ACT-ViT with LOS-Net.

\input{figs/tab7_losnet}

\paragraph{ACT-ViT performance average over three seeds.} As outlined in the NeurIPS paper checklist, we
provide additional results for ACT-ViT over the datasets and tasks provided Table~\ref{tab:main}, where we rerun
ACT-ViT with three random seeds and report the mean and standard deviation. Those results are
provided in Table~\ref{tab:seeds}.

\input{figs/tab8_seeds}

\subsection{Run-Time}
\label{app:runtime}

\input{figs/tab9_runtime}

We present the run-time of ACT-ViT(s), on a single NVIDIA L-40 GPU, compared with probing
classifiers, on each of the 15 LLM-dataset combinations considered in the paper; see Table~\ref{tab:runtime}.

\subsection{Layer/Token Visualizations}

Below we present the layer-token heatmaps, corresponding to each of the 15 LLM-dataset combination
considered in our paper. [Layer/token heatmap figures omitted -- see original paper.]

\subsection{Low-Data Regime Adaptation}
\label{app:lowdata}

Below, we present additional results in the low-data training regime for all 15 LLM--dataset combinations considered in our paper. [Per-LLM/dataset low-data figures (Figures 6--20 in the original) omitted -- see original paper.]
