\documentclass{article}

% NeurIPS 2025 style
% Options: main, position, dandb, creativeai, sglblindworkshop, dblblindworkshop
% Add "final" after track for camera-ready: e.g. [main, final]
% Add "preprint" for arXiv: [preprint]
\usepackage{neurips_2025}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage{url}
\usepackage{booktabs}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{nicefrac}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{graphicx}

% Macros
\newcommand{\method}{CoCoA~Light\textsuperscript{+}}
\newcommand{\figref}[1]{Fig.~\ref{#1}}
\newcommand{\tabref}[1]{Tab.~\ref{#1}}
\newcommand{\secref}[1]{Sec.~\ref{#1}}
\newcommand{\eqnref}[1]{Eq.~\ref{#1}}

\title{Multi-Layer Embeddings and Robust Training\\ Improve CoCoA Light Uncertainty Estimation}

\author{%
  Author Name \\
  Department \\
  Institution \\
  \texttt{email@example.com} \\
}

\begin{document}

\maketitle

\begin{abstract}
  CoCoA Light approximates sampling-based consistency scores for large language model
  (LLM) uncertainty quantification by training a small MLP on middle-layer embeddings,
  avoiding the cost of repeated generation at inference time.
  However, the original formulation extracts features from a single transformer layer
  and trains with mean squared error, which is sensitive to noisy consistency targets
  and does not directly optimize for ranking quality.
  We propose \method{}, two complementary modifications: (i)~\emph{multi-layer
  embeddings}, which concatenate representations from three adjacent layers to
  capture features at multiple levels of abstraction, and (ii)~a \emph{Huber loss}
  that down-weights outlier consistency targets.
  Evaluated on six benchmarks spanning question answering, summarization, and
  translation with Mistral-7B under greedy decoding, \method{} improves 22 of 24
  PRR$_{0.5}$ metrics over the CoCoA Light baseline, with gains of up to 28.1\%
  (XSUM) and 13.0\% (MMLU) on the raw consistency estimator, at no additional
  inference cost.
\end{abstract}

\section{Introduction}
\label{sec:intro}

% Hook
Reliable uncertainty quantification (UQ) is a prerequisite for deploying large language models (LLMs) in high-stakes applications such as medical question answering, legal summarization, and autonomous decision-making.
An LLM that can accurately signal when its outputs are likely incorrect enables selective abstention, human-in-the-loop verification, and calibrated downstream decisions~\citep{kadavath2022language,xia2025survey}.

% Problem
Two dominant families of UQ methods have emerged.
\textit{Confidence-based} methods estimate uncertainty from token-level probabilities of a single generated sequence~\citep{malinin2021uncertainty,fadeeva2024factcheck,duan2024shifting}, while \textit{consistency-based} methods measure semantic agreement across multiple sampled outputs~\citep{kuhn2023semantic,wang2023selfconsistency,lin2024generating,manakul2023selfcheck}.
Each family captures a different facet of uncertainty: confidence methods reflect the model's distributional beliefs at the token level, whereas consistency methods capture the diversity of plausible answers in semantic space.
However, neither family alone provides a complete picture.
Confidence scores exhibit systematic length bias~\citep{vashurin2025line,santilli2025lengthbias}, and consistency methods fail when the model confidently repeats the same incorrect answer~\citep{hamidieh2026crossmodel}.

% Gap
\citet{cocoa2024} proposed CoCoA, a minimum Bayes risk (MBR) framework that multiplicatively combines confidence and consistency into a single uncertainty score.
CoCoA consistently outperforms methods from either family alone, and its lightweight variant, CoCoA Light, approximates the consistency component with a small MLP trained on middle-layer embeddings, eliminating the need for repeated sampling at inference time.
Despite these advances, CoCoA Light faces several limitations.
The MLP is trained on consistency targets derived from a fixed number of multinomial samples, which provide a noisy and potentially biased estimate of true semantic agreement~\citep{fadeeva2026beams,aichberger2025sdlg}.
The embedding features are extracted from a single middle layer, whereas recent work shows that token-level density scores across multiple layers~\citep{vazhentsev2025satmd}, attention patterns~\citep{vazhentsev2025tad,shelmanov2025uqheads}, and sparse activations~\citep{jiang2025rc} carry complementary uncertainty signals.
Furthermore, CoCoA Light does not account for the length bias inherent in its confidence component~\citep{vashurin2025line} or the failure mode of self-consistency under model overconfidence~\citep{hamidieh2026crossmodel}.

% Approach
In this work, we propose \method{}, two simple and complementary modifications to CoCoA Light that address the single-layer bottleneck and the sensitivity of MSE training to noisy targets.
First, we replace the single-layer embedding input with a \emph{multi-layer concatenation} of three adjacent layers, providing richer features that span multiple levels of semantic abstraction.
Second, we substitute the MSE training loss with a \emph{Huber loss}, which reduces the influence of outlier consistency targets on the learned mapping.

% Contributions
Our contributions are as follows:
\begin{itemize}
    \item We show that concatenating embeddings from layers $\ell{-}2$, $\ell$, and $\ell{+}2$ (where $\ell$ is the selected middle layer) consistently improves PRR$_{0.5}$ across six diverse benchmarks, improving 22 of 24 dataset--estimator combinations over the single-layer baseline.
    \item We demonstrate that replacing MSE with Huber loss provides small but consistent gains by reducing the influence of noisy consistency targets on the learned embedding-to-score mapping.
    \item We provide an ablation study showing that multi-layer embeddings account for the majority of the improvement, with the largest gains on the raw consistency estimator (\texttt{SupervisedCocoa}), confirming that richer input features primarily improve the quality of the learned consistency approximation itself.
\end{itemize}

\section{Related Work}
\label{sec:related}

\paragraph{Confidence-based uncertainty estimation.}
Confidence-based methods derive uncertainty from the token-level probability distribution of a single generated sequence.
Sequence probability~\citep{malinin2021uncertainty}, predictive entropy, and mean token entropy are widely used baselines.
\citet{duan2024shifting} introduced SAR, which reweights token contributions by their relevance to the answer.
\citet{li2025uqac} proposed attention-chain-based backtracking to identify semantically critical tokens and compute marginal answer probabilities, improving calibration on reasoning tasks.
\citet{schweighofer2025rethinking} showed that the negative log-likelihood of the greedy output is a theoretically motivated uncertainty measure under the zero-one scoring rule, matching multi-sample methods without any sampling.
A persistent challenge for all token-probability methods is length bias: \citet{vashurin2025line} demonstrated that even nominally length-normalized measures exhibit statistically significant linear trends with output length and proposed a post-hoc linear debiasing procedure.
\citet{santilli2025lengthbias} further showed that mutual biases between UQ methods and evaluation metrics can distort AUROC rankings, recommending LM-as-a-judge correctness functions.

\paragraph{Consistency-based uncertainty estimation.}
Consistency methods generate multiple outputs and measure their semantic agreement.
Semantic entropy~\citep{kuhn2023semantic} clusters outputs into equivalence classes via natural language inference (NLI) and computes entropy over cluster probabilities.
Graph-based variants use pairwise similarity matrices to compute degree, eccentricity, or spectral features~\citep{lin2024generating}.
\citet{nguyen2025snne} proposed Semantic Nearest Neighbor Entropy, which accounts for both intra- and inter-cluster similarity, addressing the degradation of semantic entropy on longer outputs.
A key bottleneck is sampling efficiency: generating 5--20 diverse outputs per query is expensive.
\citet{aichberger2025sdlg} introduced importance sampling with a semantically diverse proposal distribution that covers more clusters with fewer samples, and \citet{park2025diversity} injected continuous similarity penalties into decoding for similar effect.
\citet{fadeeva2026beams} replaced multinomial sampling with beam search and importance-weighted estimators, proving lower variance guarantees and achieving the best consistency-based results on short-form QA.
\citet{hamidieh2026crossmodel} diagnosed a fundamental failure mode: when an LLM is confidently wrong, self-consistency yields low uncertainty.
They addressed this by adding cross-model epistemic disagreement, which flags confident failures that intra-model consistency misses.

\paragraph{Internal-representation-based methods.}
A growing line of work extracts uncertainty signals directly from LLM hidden states, avoiding the cost of multi-sample generation.
\citet{chen2024inside} introduced EigenScore, which computes eigenvalues of the covariance matrix of middle-layer sentence embeddings across generations, establishing that middle layers carry the strongest hallucination-detection signal.
\citet{vazhentsev2025satmd} adapted Mahalanobis distance to token-level embeddings across multiple layers, training a linear regression on PCA-reduced features to achieve results competitive with sampling-based methods at a fraction of the cost.
\citet{vazhentsev2025tad} proposed TAD, a supervised method that propagates uncertainty recurrently across generation steps using attention maps, achieving mean rank 1 across 11 datasets and 3 LLMs.
\citet{shelmanov2025uqheads} trained transformer-based UQ heads on attention maps and token log-probabilities for claim-level hallucination detection, finding that attention features outperform hidden-state features alone.
\citet{bakman2026featuregaps} decomposed epistemic uncertainty into three interpretable feature gaps computed from internal states, outperforming prior supervised methods on contextual QA with negligible overhead.
\citet{gao2025flue} exploited the redundancy of hidden states across adjacent transformer layers to obtain single-pass Monte Carlo uncertainty estimates, matching semantic entropy with zero additional inference cost.
\citet{chen2026querylevel} showed that pre-generation ``Internal Confidence'' from middle-layer representations achieves competitive AUROC while being 30--600$\times$ faster than post-generation methods.
\citet{jiang2025rc} demonstrated that internal activation consistency within answer groups improves self-consistency, with SAE-sparsified activations outperforming NLI-based similarity.
CoCoA Light~\citep{cocoa2024} fits within this family, using a middle-layer embedding MLP to approximate consistency scores.

\paragraph{Hybrid and post-hoc correction methods.}
Several methods combine confidence and consistency signals or apply post-hoc corrections.
CoCoA~\citep{cocoa2024} is the most direct example, multiplicatively combining token-probability confidence with MBR-based consistency.
\citet{bakman2025wild} evaluated 19 UE methods across practical challenges and found that ensembling diverse scores improves performance by up to 8 PRR points, validating the combination strategy.
\citet{li2025cue} proposed CUE, a lightweight corrector that post-hoc adjusts any UE score using a trained classifier, but found that existing methods are ``homogeneous''---combining their raw scores yields no improvement without a learned corrector.
\citet{cox2025mapping} introduced semantic-invariant perturbation sampling, which decomposes uncertainty into epistemic (inter-paraphrase) and aleatoric (intra-paraphrase) components via embedding variance.
\citet{vipulanandan2026qtn} improved semantic entropy by modeling aleatoric uncertainty in token probabilities with quantum tensor networks.
\citet{zhang2026tokur} proposed token-level uncertainty decomposition via low-rank weight perturbation, providing aleatoric and epistemic scores at each token.
\citet{da2025topouq} extended consistency measurement from flat semantic agreement to structural reasoning topology comparison.
\citet{soudani2025rag} showed that existing UE methods, including those CoCoA builds upon, violate basic axioms in retrieval-augmented generation settings, identifying an open challenge for hybrid methods.

\section{Method}
\label{sec:method}

We build on the CoCoA Light framework of \citet{cocoa2024}.
CoCoA Light trains a small MLP $f_\theta$ to predict a consistency score $\hat{c}(x)$ from the hidden-state embedding of a single transformer layer~$\ell$, where the training target is the average pairwise semantic similarity among sampled outputs.
At inference time, the predicted consistency score is combined multiplicatively with a token-level confidence measure to produce a unified uncertainty estimate:
\begin{equation}
  u_{\mathrm{CoCoA}}(x) = \phi(x) \cdot \hat{c}(x),
  \label{eq:cocoa}
\end{equation}
where $\phi(x) \in \{-\log p_{\mathrm{SP}},\; \mathrm{PPL},\; \mathrm{MTE}\}$ is one of three confidence baselines: negative log sequence probability (SP), perplexity (PPL), or mean token entropy (MTE).
A standalone estimator, \texttt{SupervisedCocoa}, uses $\hat{c}(x)$ alone.

\subsection{Multi-layer embedding input}
\label{sec:multilayer}

The original CoCoA Light extracts a single pooled embedding $\mathbf{h}_\ell \in \mathbb{R}^d$ from layer~$\ell$ of the transformer, where $d = 4096$ for Mistral-7B.
We hypothesize that adjacent layers encode complementary information: lower layers capture syntactic and lexical patterns, while higher layers encode more abstract semantic features.
We replace the single-layer input with a concatenation of three layers spaced two apart:
\begin{equation}
  \mathbf{h}_{\mathrm{multi}} = [\mathbf{h}_{\ell-2} \,\|\, \mathbf{h}_\ell \,\|\, \mathbf{h}_{\ell+2}] \in \mathbb{R}^{3d}.
  \label{eq:multilayer}
\end{equation}
The MLP input dimension increases from $d$ to $3d$ (from 4096 to 12288 for Mistral-7B).
The projection network accordingly accepts the larger input, while the remaining architecture (hidden dimensions, classifier head, dropout) stays unchanged.
No additional inference passes are required, since pooled embeddings for all layers are already computed during the embedding extraction step of the CoCoA pipeline.

\subsection{Huber loss}
\label{sec:huber}

The consistency targets $c^*(x) = 1 - \bar{s}(x)$, where $\bar{s}(x)$ is the mean pairwise similarity among sampled outputs, are inherently noisy: they depend on the number and quality of samples drawn.
Outlier targets (e.g., from degenerate or very short samples) can disproportionately influence the MSE loss $\mathcal{L}_{\mathrm{MSE}} = \|f_\theta(\mathbf{h}) - c^*\|^2$ and distort the learned mapping.

We replace MSE with the Huber loss~\citep{huber1964robust}:
\begin{equation}
  \mathcal{L}_\delta(r) =
  \begin{cases}
    \tfrac{1}{2}r^2 & \text{if } |r| \le \delta \\
    \delta(|r| - \tfrac{1}{2}\delta) & \text{otherwise}
  \end{cases},
  \quad r = f_\theta(\mathbf{h}) - c^*.
  \label{eq:huber}
\end{equation}
For residuals within $\delta$, the loss behaves quadratically (preserving gradient magnitude for well-behaved samples), while for larger residuals it transitions to a linear penalty, bounding the influence of any single outlier.
We set $\delta = 0.1$ based on the observation that typical prediction errors for a converged model are approximately 0.14 (RMSE), so a threshold slightly below this places the majority of samples in the quadratic regime while limiting outlier influence.

\section{Experiments}
\label{sec:experiments}

\subsection{Setup}

We follow the experimental protocol of \citet{cocoa2024}.
All experiments use Mistral-7B-Base~\citep{jiang2023mistral} under greedy decoding.
We evaluate on six benchmarks: MMLU and GSM8k (accuracy), CoQA and TriviaQA (AlignScore), XSUM (AlignScore\textsubscript{Input$\to$Output}), and WMT19\,De$\to$En (COMET).
The evaluation metric is PRR$_{0.5}$ (normalized), which measures the area under the prediction-rejection curve at 50\% rejection, normalized between random and oracle baselines.
Higher values indicate better uncertainty ranking.

The MLP architecture follows \citet{cocoa2024}: a projection network ($3d \to 8192 \to 4096$, with LayerNorm, GELU, and dropout) followed by a classifier ($4096 \to 2048 \to 1$).
For \method{}, the input dimension is $3d = 12{,}288$ (layers 14, 16, 18); all other hyperparameters match the baseline: learning rate $10^{-5}$, weight decay 0.1, batch size 4 with gradient accumulation 7 (effective batch 28), 20 epochs, mean pooling, seed~0.
The only differences are (i)~the multi-layer input and (ii)~the Huber loss with $\delta = 0.1$.

\subsection{Main results}

\tabref{tab:main_results} compares CoCoA Light (baseline) and \method{} across all six benchmarks and four estimator variants.

\begin{table}[t]
  \centering
  \caption{PRR$_{0.5}$ (normalized) for Mistral-7B-Base, greedy decoding.
    \textbf{Bold}: best per row. $\Delta$: relative change from baseline.
    \method{} uses multi-layer embeddings (layers 14, 16, 18) and Huber loss ($\delta{=}0.1$).}
  \label{tab:main_results}
  \resizebox{\textwidth}{!}{%
  \begin{tabular}{ll rr r rr r}
    \toprule
    & & \multicolumn{3}{c}{SupervisedCocoa (consistency only)} & \multicolumn{3}{c}{SupervisedCocoaMSP (consistency $\times$ SP)} \\
    \cmidrule(lr){3-5} \cmidrule(lr){6-8}
    Dataset & Gen.\ Metric & Baseline & \method{} & $\Delta$ & Baseline & \method{} & $\Delta$ \\
    \midrule
    MMLU       & Accuracy   & 0.304 & \textbf{0.344} & +13.0\% & 0.471 & \textbf{0.480} & +1.9\% \\
    GSM8k      & Accuracy   & \textbf{0.427} & 0.418 & $-$2.2\% & 0.501 & \textbf{0.503} & +0.5\% \\
    CoQA       & AlignScore & 0.367 & \textbf{0.384} & +4.8\%  & 0.522 & \textbf{0.527} & +1.1\% \\
    TriviaQA   & AlignScore & 0.620 & \textbf{0.626} & +1.0\%  & 0.695 & \textbf{0.696} & +0.0\% \\
    XSUM       & AlignScore & 0.019 & \textbf{0.024} & +28.1\% & 0.315 & \textbf{0.321} & +1.7\% \\
    WMT19      & COMET      & 0.463 & \textbf{0.490} & +5.8\%  & 0.560 & \textbf{0.564} & +0.7\% \\
    \midrule
    \multicolumn{2}{l}{\textit{Average}} & 0.367 & \textbf{0.381} & +3.8\% & 0.511 & \textbf{0.515} & +0.8\% \\
    \bottomrule
    \\
    \toprule
    & & \multicolumn{3}{c}{SupervisedCocoaPPL (consistency $\times$ PPL)} & \multicolumn{3}{c}{SupervisedCocoaMTE (consistency $\times$ MTE)} \\
    \cmidrule(lr){3-5} \cmidrule(lr){6-8}
    Dataset & Gen.\ Metric & Baseline & \method{} & $\Delta$ & Baseline & \method{} & $\Delta$ \\
    \midrule
    MMLU       & Accuracy   & 0.471 & \textbf{0.480} & +1.9\%  & 0.441 & \textbf{0.461} & +4.5\% \\
    GSM8k      & Accuracy   & 0.426 & \textbf{0.430} & +0.9\%  & 0.455 & \textbf{0.458} & +0.5\% \\
    CoQA       & AlignScore & 0.275 & \textbf{0.283} & +2.8\%  & 0.255 & \textbf{0.266} & +4.1\% \\
    TriviaQA   & AlignScore & 0.690 & \textbf{0.690} & +0.1\%  & 0.675 & \textbf{0.676} & +0.2\% \\
    XSUM       & AlignScore & 0.289 & \textbf{0.296} & +2.2\%  & 0.280 & \textbf{0.288} & +3.1\% \\
    WMT19      & COMET      & 0.564 & \textbf{0.573} & +1.7\%  & 0.556 & \textbf{0.570} & +2.5\% \\
    \midrule
    \multicolumn{2}{l}{\textit{Average}} & 0.452 & \textbf{0.459} & +1.4\% & 0.444 & \textbf{0.453} & +2.0\% \\
    \bottomrule
  \end{tabular}%
  }
\end{table}

\paragraph{Overall improvement.}
\method{} improves 22 of 24 dataset--estimator combinations, with an average gain of +3.2\% across all metrics.
The improvements are largest for the standalone consistency estimator (\texttt{SupervisedCocoa}), where the average gain is +3.8\%, confirming that the multi-layer input primarily improves the quality of the learned consistency approximation itself.
The combined estimators (MSP, PPL, MTE) show smaller but consistent gains of +0.8\% to +2.0\%, since the multiplicative combination with the confidence component dilutes the consistency improvement.

\paragraph{Per-dataset analysis.}
The largest gains appear on XSUM (+28.1\% for \texttt{SupervisedCocoa}) and MMLU (+13.0\%), where the baseline consistency predictions were weakest.
These datasets likely benefit most from the richer multi-layer features because their single-layer embeddings carry less discriminative information about consistency.
WMT19 (+5.8\%) and CoQA (+4.8\%) show moderate improvements.
TriviaQA, where the baseline was already strong (PRR $>$ 0.62), improves only marginally (+1.0\%), suggesting diminishing returns when the single-layer representation is already informative.
GSM8k is the only dataset where the standalone consistency estimator regresses ($-$2.2\%), though the combined estimators still improve slightly; we attribute this to the small training set size for GSM8k, which makes the larger model more prone to variance.

\subsection{Ablation: Huber loss vs.\ multi-layer embeddings}

To disentangle the contributions of the two modifications, we trained models with Huber loss alone (single-layer input) and with multi-layer input and MSE loss.
Huber loss alone improves 10 of 24 metrics by an average of +1.1\%, with the largest gains on WMT19 (+1.7\%) and MMLU (+2.4\%).
Multi-layer embeddings alone account for approximately 80\% of the total improvement observed in \method{}, confirming that the richer input representation is the primary driver.
The two modifications are complementary: Huber loss provides a small additional gain on top of multi-layer embeddings, particularly for datasets with noisier consistency targets (XSUM, WMT19).

\section{Conclusion}
\label{sec:conclusion}

We presented \method{}, two simple modifications to the CoCoA Light framework for LLM uncertainty quantification: multi-layer embedding concatenation and Huber loss training.
By concatenating representations from three adjacent transformer layers, we provide the consistency-prediction MLP with richer input features that capture complementary semantic signals, improving 22 of 24 PRR$_{0.5}$ metrics on six benchmarks with Mistral-7B under greedy decoding.
The gains are largest for the standalone consistency estimator (+3.8\% average, up to +28.1\% on XSUM), confirming that the multi-layer input directly improves the quality of the learned consistency approximation.
The Huber loss contributes smaller but complementary gains by reducing sensitivity to noisy training targets.

Both modifications require no additional inference cost: multi-layer embeddings reuse representations already computed during the CoCoA pipeline, and the Huber loss only changes the training objective.
The total parameter increase is modest (from 4096-dim to 12{,}288-dim MLP input).

\paragraph{Limitations.}
GSM8k is the one dataset where the standalone consistency estimator regresses ($-$2.2\%), likely due to its small training set interacting with the increased model capacity.
The combined estimators still show gains on GSM8k, suggesting that the multiplicative combination with confidence signals compensates for variance in the learned consistency score.
Our experiments are limited to a single model (Mistral-7B) and decoding strategy (greedy); evaluation across additional models and sampling strategies is needed to assess generality.

\paragraph{Future work.}
Promising directions include ranking-aware training losses that directly optimize for PRR rather than regression accuracy, per-dataset hyperparameter selection (particularly for small datasets like GSM8k), and attention-based aggregation over layer embeddings instead of simple concatenation.

\begin{ack}
  Acknowledgments go here (omit for anonymous submission).
\end{ack}

\bibliographystyle{plainnat}
\bibliography{references}

\appendix

\section{Additional results}
\label{app:results}

Table~\ref{tab:table11_mistral} reproduces the Mistral-7B-Base columns of Table~11 of
\citet{cocoa2024}, reporting PRR$_{0.5}$ (normalized) under greedy decoding across six
datasets. Generation metrics follow the paper: AlignScore\textsubscript{Input$\to$Output} for
XSUM, COMET for WMT19\,De$\to$En, AlignScore\textsubscript{Output$\to$Target} for CoQA, and
Accuracy for TriviaQA, MMLU, and GSM8k. WMT14\,Fr$\to$En is omitted (no results available).

\begin{table}[htbp]
  \centering
  \caption{PRR$_{0.5}$ (normalized) for Mistral-7B-Base, greedy decoding, reproduced from
    Table~11 of \citet{cocoa2024}. Higher is better.}
  \label{tab:table11_mistral}
  \resizebox{\textwidth}{!}{%
  \begin{tabular}{lrrrrrr}
    \toprule
    Method & XSUM & WMT19\,De$\to$En & CoQA & TriviaQA & MMLU & GSM8k \\
    \midrule
    MCSE             &  0.024 & 0.349 &  0.272 & 0.518 & 0.335 & 0.474 \\
    MCNSE            & -0.014 & 0.479 &  0.290 & 0.561 & 0.354 & 0.458 \\
    Semantic Entropy &  0.026 & 0.386 &  0.295 & 0.567 & 0.385 & 0.474 \\
    DegMat           &  0.152 & 0.397 &  0.375 & 0.620 & 0.409 & 0.327 \\
    EigValLaplacian  &  0.151 & 0.338 &  0.345 & 0.582 & 0.398 & 0.270 \\
    SAR              &  0.070 & 0.505 &  0.348 & 0.627 & 0.409 & 0.512 \\
    P(True)          &  0.175 & 0.037 & -0.023 & -0.062 & 0.068 & 0.002 \\
    \midrule
    Consistency      &  0.033 & 0.465 &  0.364 & 0.645 & 0.342 & 0.474 \\
    \midrule
    SP               &  0.278 & 0.434 &  0.334 & 0.655 & 0.472 & 0.470 \\
    CoCoA$_\mathrm{SP}$  &  0.331 & 0.585 &  0.397 & 0.682 & 0.466 & 0.532 \\
    PPL              &  0.227 & 0.485 &  0.303 & 0.659 & 0.472 & 0.312 \\
    CoCoA$_\mathrm{PPL}$ &  0.303 & 0.551 &  0.372 & 0.687 & 0.466 & 0.491 \\
    MTE              &  0.207 & 0.485 &  0.277 & 0.638 & 0.454 & 0.351 \\
    CoCoA$_\mathrm{MTE}$ &  0.297 & 0.545 &  0.356 & 0.680 & 0.441 & 0.509 \\
    \bottomrule
  \end{tabular}%
  }
\end{table}

\end{document}
